\documentclass[12pt]{article}
\title{}
\date{}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathrsfs}
\usepackage{times}
\usepackage{diagcat}
%\usepackage{hyperref}
%\usepackage{CJKutf8}
\textwidth=16cm
\textheight=23cm
\voffset=-1.8cm
\hoffset=-1.1cm
%------------------------------------------------------------------------------%
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{Ex}{Example}
\newtheorem*{ex}{Exercise}

\newcommand{\ba}{\beta}
\newcommand{\da}{\delta}
\newcommand{\Da}{\Delta}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\la}{\lambda}
\newcommand{\Oa}{\Omega}
\newcommand{\vphi}{\varphi}

\newcommand{\pl}{\partial}
\newcommand{\fc}{\frac}
\newcommand{\na}{\nabla}
\newcommand{\ol}{\overline}
\newcommand{\lt}{\left}
\newcommand{\rt}{\right}
\newcommand{\rw}{\rightarrow}

\newcommand{\mf}{\mathbf}
\newcommand{\mb}{\mathbb}
\newcommand{\ml}{\mathcal}

\newcommand{\bs}{\boldsymbol}
\newcommand{\wt}{\widetilde}

\pagestyle{empty}

\begin{document}
\begin{center}
{\Large \bf Exercises for Week 5}
\end{center}
The work handed in should be entirely your own. You can consult Dummit and Foote, Artin and/or the class notes but nothing else. To receive full credit, justify your answer in a clear and logical way. Due Oct. 9.

\paragraph{Reading.} With Dummit and Foote, please read Sections 1.6, 3.1, 3.2.  Alternatively, read Artin Sections 2.5, 2.6.

\begin{enumerate}
\item Let $f:(\mathbb{R},+)\to (\mathbb{C}^*,\times)$ be the map $f(a)=e^{2\pi i a}$. Prove that it's a group homomorphism and determine its kernel and image.
\item Let $G$ be a group and $x\in G$ be an element of finite order $n$. Show that
$$\phi_x: \mathbb{Z}/(n)\longrightarrow \langle x \rangle, \quad \overline{a}\mapsto x^a$$
is a well-defined group homomorphism, i.e., it's independent of representatives you choose for $\overline{a}$. Then prove that $\phi_x$ is an isomorphism.
%\item In class we have shown that there is a bijection of sets
%$$G\cong \mathrm{Hom}_{\mathrm{Group}}(\mathbb{Z},G), \quad x \mapsto \left(\phi_x:a\mapsto x^a\right).$$
% Now we will consider $\mathrm{Hom}_{\mathrm{Group}}(\mathbb{Z}/(n),G)$.\\
%    (a). Prove that given any element $x\in G$, such that $x^n=1$, then the
\item For $S_3$, and $
g=(12)=
\begin{DGCpicture}[scale=0.5]
\DGCstrand(0,0)(1,1)
\DGCstrand(1,0)(0,1)
\DGCstrand(2,0)(2,1)
\end{DGCpicture}$,
write out explicitly what the conjugation-isomorphism-by-$g$ does to all elements of $S_3$.
\item Prove that there is an isomorphism of groups
$$U(1):=\left\{z\in \mathbb{C}^*\big||z|=1\right\}\cong SO(2, \mathbb{R}):=
\left\{
\left(
\begin{array}{cc}
\cos \theta & -\sin \theta\\
\sin \theta & \cos \theta
\end{array}
\right)
\big|
\theta \in \mathbb{R}
\right\},
$$
by explicitly constructing the isomorphisms.
\item Let $\phi \colon \mathbb{Z}/(12) \mapsto \mathbb{Z}/(3), \overline{a}\mapsto \overline{a}$. Prove that this is a well-defined group homomorphism, and find its kernel.
\item (a) Prove that if $K $ is a normal subgroup of $G$, and $H$ is an arbitrary subgroup of $G$, then $K\cap H \lhd H$.\\
(b) If $\phi: G\to G^\prime$ is a group homomorphism, and $H$ is a subgroup of $G$. Use the previous part to determine that under what condition the restriction $\phi|_H: H\to G^\prime$ is an injective homomorphism.
\item For $S_3$ and its normal subgroup $A_3$, write out the $2\times 2$ multiplication table for the cosets (quotient group) $S_3/A_3$. Identify it with a more familiar group.
\item Prove that in any group $G$, and given elements $a,b\in G$, there is a conjugation automorphism of $G$ taking $ab$ into $ba$.
\end{enumerate}
\end{document} 