\documentclass[12pt]{article}
\title{}
\date{}
\usepackage{amsmath,amsfonts,amsthm,amssymb,mathrsfs}
\usepackage{times}
\usepackage{diagcat}
%\usepackage{hyperref}
%\usepackage{CJKutf8}
\textwidth=16cm
\textheight=23cm
\voffset=-1.8cm
\hoffset=-1.1cm
%------------------------------------------------------------------------------%
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{Ex}{Example}
\newtheorem*{ex}{Exercise}

\newcommand{\ba}{\beta}
\newcommand{\da}{\delta}
\newcommand{\Da}{\Delta}
\newcommand{\ta}{\theta}
\newcommand{\Ta}{\Theta}
\newcommand{\la}{\lambda}
\newcommand{\Oa}{\Omega}
\newcommand{\vphi}{\varphi}

\newcommand{\pl}{\partial}
\newcommand{\fc}{\frac}
\newcommand{\na}{\nabla}
\newcommand{\ol}{\overline}
\newcommand{\lt}{\left}
\newcommand{\rt}{\right}
\newcommand{\rw}{\rightarrow}

\newcommand{\mf}{\mathbf}
\newcommand{\mb}{\mathbb}
\newcommand{\ml}{\mathcal}

\newcommand{\bs}{\boldsymbol}
\newcommand{\wt}{\widetilde}

\pagestyle{empty}

\begin{document}
\begin{center}
{\Large \bf Exercises for Week 6}
\end{center}
The work handed in should be entirely your own. You can consult Dummit and Foote, Artin and/or the class notes but nothing else. To receive full credit, justify your answer in a clear and logical way. Due Oct. 16.

\paragraph{Reading.} With Dummit and Foote, please read Sections 3.1, 3.2.  Alternatively, read Artin Section 2.12.

\begin{enumerate}
\item Consider $S_{n-1}\subset S_n$ as permutations of the first $n-1$ letters. Show that $S_{n-1}$ is not a normal subgroup.
\item If $H$, $K$ are two groups, show that $H\times \{1_K\}, \{1_H\}\times K $ are normal subgroups of $ H \times K$. Identify the corresponding quotient groups.
\item In the general linear group $GL_3(\mathbb{R})$, consider the subgroups
$$H:=
\left\{
\left(
\begin{array}{ccc}
1 & a & b\\
0 & 1 & c\\
0 & 0 & 1
\end{array}
\right)
\Big|
a, b, c \in \mathbb{R}
\right\}, \quad \quad
K:=
\left\{
\left(
\begin{array}{ccc}
1 & 0 & a\\
0 & 1 & 0\\
0 & 0 & 1
\end{array}
\right)
\Big|
a \in \mathbb{R}
\right\},
$$
Show that $K$ is a normal subgroup of $H$, and identify the quotient group with a more elementary one.
\item Let $H$ and $K$ be subgroups of a group $G$. Show that the intersection $xH\cap yK$ of two cosets of $H$ and $K$ is either empty or else a coset for the subgroup $H\cap K$.
\end{enumerate}
\end{document} 